### 2015-12-11 fundamentals/fcsreqs.tex

A final benefit of the discreteness of facilities and materials is their power
when combined. The ability to track a material's history as it moves from one
facility to another is unique to \Cyclus. While some current simulators track
materials in discrete quanta, they do not necessarily preserve the identity of each quantum as the
materials move around the fuel cycle. When coupled with \Cyclus' individual
facility modeling, this capacity becomes distinct from what other fuel cycle
simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
whether a batch being discharged from a reactor originated in \gls{MOX}
fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
tracking which of the fresh batches contained material from a particular
discharged batch. By extension, \Cyclus can also report which individual
facilities the batch passed through and in which it originated. The
nonproliferation-related applications of this analysis capability are
significant - allowing \Cyclus to answer questions that previous simulators
have been unable to ask.

>>>>

A final benefit of the discreteness of facilities and materials is their power
when combined. The ability to track a material's history as it moves from one
facility to another is unique to \Cyclus. While some current simulators track
materials in discrete quanta, they do not necessarily preserve the identity of each quantum as the
materials move around the fuel cycle. When coupled with \Cyclus' individual
facility modeling, this capacity becomes distinct from what other fuel cycle
simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
whether a batch being discharged from a reactor originated in \gls{MOX}
fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
tracking which of the fresh batches contained material from a particular
discharged batch. By extension, \Cyclus can also report which individual
facilities the batch passed through and in which it originated. 
The ability to track a single material through the simulation, 
though it might be split, transmuted, or merged with other materials along the 
way, allows \Cyclus to answer more data-rich questions that previous simulators
have been unable to ask. For example, it allows precise tracking of 
specific material diversions, so queries about nonproliferation 
robustness in a facility can be levied either in the context of a single event or 
a series of nefarious acts.

### 2015-12-11 fundamentals/impl.tex

Furthermore, the \gls{ABM} paradigm more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

Autmated testing including \gls{CI} is a necessary but not sufficient
component of the \Cyclus \gls{QA} system: it keeps bad code out of
\Cyclus. However, \Cyclus will always require human eyes and hands to let good
code in.

>>>>

Furthermore, the \gls{ABM} paradigm is more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

Automated testing including \gls{CI} is a necessary but not sufficient
component of the \Cyclus \gls{QA} system: it keeps bad code out of
\Cyclus. However, \Cyclus will always require human eyes and hands to let good
code in.
